DMRGenie: Graphical interface for entanglement renormalization

### 2025-11-26 paper/paper.tex
Update paper.tex

On one hand, for ideas to be implemented computationally, a need arises for easy-to-use high level languages. "On the other hand, scientific programming often requires computational resources at scale, driving optimization and performance requirements. To accomplish this second demand, a low-level language is required to control as much as possible in an implementation of an algorithm. This split between needs for different programming projects is known as the two-language problem.

@@

Quantum information methods have become a tantalizing path to creating new algorithms and methods. These range from quantum algorithms implemented on quantum computers \cite{nielsen2010quantum} (but since no perfect quantum computer exist, simulations with classical methods are still required) to entanglement renormalization techniques.\footnote{This class of methods is more commonly referred to as tensor networks, simply, but with the rise of machine-learning and other methods particularly in quantum chemistry that are formulated on tensor networks, a distinguishing name is required. We choose to expand the usage of the term from Ref.~\cite{vidal2007entanglement} since all methods are fundamentally optimizing over quantities relevant for quantum information ({\it i.e.}, the entanglement) and renormalization was originally introduced to describe this class of methods \cite{wilson1983renormalization,krishna1980renormalization}. The methods required to implement an algorithm in this context is different from other contexts, notably machine learning.}

>>>>

On one hand, for ideas to be implemented computationally, a need arises for easy-to-use high level languages. On the other hand, scientific programming often requires computational resources at scale, driving optimization and performance requirements. To accomplish this second demand, a low-level language is required to control as much as possible in an implementation of an algorithm. This split between needs for different programming projects is known as the two-language problem.

@@

Quantum information methods have become a tantalizing path to creating new algorithms and methods. These range from quantum algorithms implemented on quantum computers \cite{nielsen2010quantum} (but since no perfect quantum computer exists as of yet, so simulations with classical methods are still required) to entanglement renormalization techniques.\footnote{This class of methods is more commonly referred to as tensor networks, simply, but with the rise of machine-learning and other methods particularly in quantum chemistry that are formulated on tensor networks, a distinguishing name is required. We choose to expand the usage of the term from Ref.~\cite{vidal2007entanglement} since all methods are fundamentally optimizing over quantities relevant for quantum information ({\it i.e.}, the entanglement) and renormalization was originally introduced to describe this class of methods \cite{wilson1983renormalization,krishna1980renormalization}. The methods required to implement an algorithm in this context is different from other contexts, notably machine learning.}
